probKanren: A Simple Probabilistic extension for microKanren

### 2021-09-15 paper/main.tex
Give a definition for r

The above is called multinomial resampling but there are other methods
as well. A survey\cite{douc2005comparison} of resampling methods
suggests all of them are helpful to reduce particle degeneracy.

>>>>

We set $r(w) = \text{Categorical}(w)$, which is called multinomial resampling but there are other methods
as well\cite{douc2005comparison}.
